---
title: "Results_Final"
author: "Felicia Zhang"
date: "10/18/2016"
output: html_document
---

1. Prepare Data
```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)

#load data
#orig = read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/AV_Mixed/Data/V2/AVMix_final.csv")  
#orig$X <- NULL
orig = readRDS("/Volumes/emberson/ResearchProjects/Pupillometry/AV_Mix/Data/V2/AVMix.rds")
#orig is only samples where Ss are looking at center of screen, ~ 400 x 400 box

#colors
grouptrial <- c("#333333", "#CC0066","#FF6600","#FFcc66","#666666","#999999")
colorAV <- c("#333333", "#CC0066")
colorA <- c("#FF6600","#666666")
colorV <- c("#FFcc66","#999999")
colorVom <- c("#CC0066", "#FF6600")
colorAom <- c("#CC0066", "#FFcc66")
colortimes <- c("#0099FF", "#0033FF")
#trialtype (1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
#screen dimensions of screen are 1280 x 1024 and image itself is 250 x 250 pixels 

#poo4 = matching number of times seen
poo4 <- subset(orig, timesseen < 16)
```

Looking percent per subject
```{r }
#1. calculate trackloss
subs <- unique(poo2$subID)
#create new data frame 
zoo <- data.frame(subID=numeric(),percentlooking=numeric())

for (j in 1:length(subs)){
  z <- subset(poo2, subID == subs[j])
  notlooking <- length(which(is.na(z$RIGHT_PUPIL_SIZE)))
  notlookingpercent <- notlooking / length(z$RECORDING_SESSION_LABEL)
  lookingpercent <- 1 - notlookingpercent
  zz <- c(subs[j],lookingpercent)
  zoo <- rbind(zoo,zz)
}
names(zoo)[1] <- "subID"
names(zoo)[2] <- "percentlooking"
zoo$percentlooking <- as.numeric(zoo$percentlooking)
#2. plot

ggplot(zoo,aes(x=factor(subID),y=percentlooking))+
    theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+ggtitle("Looking percentage per subject")+
  labs(x = "Subject ID", y = "Percent Looking")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  geom_hline(yintercept = mean(zoo$percentlooking), size =1,color = "red")+
  geom_hline(yintercept = 0.5, size =1,color = "green")
```

X and Y coordinate for each subject and each trial type
```{r}
#0-1000ms
hoo1 <- subset(poo2, TIMECODE < 1001)
#calculation avg gaze x and gaze y position during that period
doo <- group_by(hoo1, subID,trialtype) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y,na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo,aes(x=meanX,y=meanY,color=factor(trialtype)))+
  geom_point()+ggtitle("Gaze position for every subject (0-1000ms)")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+scale_color_manual(values=grouptrial,name="Trial Type", breaks=c("1", "2","3","4","5","6"),labels=c("A1V1", "A2V2", "A2--","--V2","A3--","--V3"))

#1000-2000
hoo2 <- subset(poo2, TIMECODE > 999 & TIMECODE < 2001)

doo2 <- group_by(hoo2,subID,trialtype) %>%
  summarise(
    meanY=mean(RIGHT_GAZE_Y,na.rm = TRUE),
    meanX=mean(RIGHT_GAZE_X,na.rm = TRUE)
  )

ggplot(doo2,aes(x=meanX,y=meanY,color=factor(trialtype)))+
  geom_point()+ggtitle("Gaze position for every subject (1000-2000ms)")+
  labs(x = "X coordinate", y = "Y coordinate")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,300),position="top")+
  scale_y_reverse(limits = c(1024, 0))+scale_color_manual(values=grouptrial,name="Trial Type", breaks=c("1", "2","3","4","5","6"),labels=c("A1V1", "A2V2", "A2--","--V2","A3--","--V3"))

```

MAKE PLOTS ACCORDING TO KOENIG ANALYSIS

#cue = audio, outcome = visual

trial types: trialtype (1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
average PDR
X: block
Y: pupil change
facet wrap by trial type
```{r}
#only care about first 4000ms
#2s + 4.6s min
poo5 <- subset(poo4, TIMECODE > 999 & TIMECODE < 3001)
poo5$block <- 1 #12
poo5$block[poo5$timesseen > 3 & poo5$timesseen < 7] <- 2 #4 5 6
poo5$block[poo5$timesseen > 6 & poo5$timesseen < 10] <- 3 #7 8 9
poo5$block[poo5$timesseen > 9 & poo5$timesseen < 13] <- 4 #10 11 12
poo5$block[poo5$timesseen > 12] <- 5 #13 14 15

doo <- group_by(poo5,subID,block,trialtype) %>%
  summarise(
    avg.pupilSs=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
doo2 <- group_by(doo,block,trialtype) %>%
  summarise(
    avg.pupil=mean(avg.pupilSs,na.rm = TRUE),
    sePupil=sd(avg.pupilSs, na.rm = TRUE)/sqrt(length(avg.pupilSs))
  )

#only care about A1V1, A2V2, A3-- or 1,2,5
doo3<-doo2[!(doo2$trialtype==3 | doo2$trialtype==4 | doo2$trialtype==6),]
doo3$label <- doo3$trialtype
doo3$label[doo3$trialtype==5] <- 1 #trialtype5 = A3--
doo3$label[doo3$trialtype==1] <- 3 #trialtype1 = A1V1

#facet wrap
label <- c(`1` = "Low uncertainty, low reward",`2` = "High uncertainty, moderate reward",`3` = "Low uncertainty, high reward")
ggplot(doo3,aes(x=block,y=avg.pupil,fill=factor(label),colour=factor(label)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials per block)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(-0.05,.15),breaks=seq(-0.05,0.15,0.02))+
  theme(legend.position="none")+
  facet_wrap(~label,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_fill_manual(values=c("#2a92ff", "#ff15ff", "#559455"))+
  scale_color_manual(values=c("#2a92ff", "#ff15ff", "#559455"))

#all trialtypes
#(1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
label <- c(`1` = "A1V1",`2` = "A2V2",`3` = "A2--",`4` = "--V2",`5` = "A3--",`6` = "--V3")
ggplot(doo2,aes(x=block,y=avg.pupil,fill=factor(trialtype),colour=factor(trialtype)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials/block)", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(legend.position="none")+
  facet_wrap(~trialtype,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_y_continuous(labels=percent,limits=c(-0.1,.15),breaks=seq(-0.1,0.15,0.05))

```

Stats:
1. ANOVA trialtype x block
2.t-test for each condition
```{r}
#Two Within Factors W1 W2, Two Between Factors B1 B2 
#fit <- aov(y~(W1*W2*B1*B2)+Error(Subject/(W1*W2))+(B1*B2), data=mydataframe)
foo <- group_by(poo5,subID,block,trialtype) %>%
  summarise(
    avg.pupilSs=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
foo2<-foo[!(foo$trialtype==3 | foo$trialtype==4 | foo$trialtype==6),] 
foo2$subID <- as.factor(foo2$subID)
fit <- aov(avg.pupilSs~trialtype*block + Error(subID/(trialtype*block)),data=foo2)
summary(fit)

#main effect of trial type p = 0.00428
#no effect of block p = 0.4765
#no interaction p = 0.8447

######### Correlation #########
foo3 <- group_by(foo2,block,trialtype) %>%
  summarise(
    avg.pupil=mean(avg.pupilSs,na.rm = TRUE),
    sePupil=sd(avg.pupilSs, na.rm = TRUE)/sqrt(length(avg.pupilSs))
  )

a <- subset(foo3, trialtype==1) #high reward
cor.test(a$block, a$avg.pupil, alternative = "two.sided", method = "pearson")
#t = -0.63828, df = 3, p-value = 0.5687, r = -0.345

b <- subset(foo3, trialtype==2) #mod reward
cor.test(b$block, b$avg.pupil, alternative = "two.sided", method = "pearson")
#t = 2.9963, df = 3, p-value = 0.05784, r = 0.865 *

c <- subset(foo3, trialtype==5) #low reward
cor.test(c$block, c$avg.pupil, alternative = "two.sided", method = "pearson")
#t = -2.628, df = 3, p-value = 0.07846, r = -0.835 *


##############
doo$subID <- as.factor(doo$subID)
fit2 <- aov(avg.pupilSs~trialtype*block + Error(subID/(trialtype*block)),data=doo)
summary(fit2)
```

trial types: trialtype (1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
timecourse plot
X: time
Y: pupil change
facet wrap early vs late block (1 vs 5)
```{r}
poo5 <- subset(poo4, TIMECODE > 999 & TIMECODE < 3001)
poo5$block <- 1 #12
poo5$block[poo5$timesseen > 3 & poo5$timesseen < 7] <- 2 #4 5 6
poo5$block[poo5$timesseen > 6 & poo5$timesseen < 10] <- 3 #7 8 9
poo5$block[poo5$timesseen > 9 & poo5$timesseen < 13] <- 4 #10 11 12
poo5$block[poo5$timesseen > 12] <- 5 #13 14 15

poo6 <- subset(poo5, block==1 | block==5) #only comparing block 1 and 5
doo <- group_by(poo6,subID,TIMECODE,block,trialtype) %>%
  summarise(
    avg.pupilSs=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
doo2 <- group_by(doo,TIMECODE,block,trialtype) %>%
  summarise(
    avg.pupil=mean(avg.pupilSs,na.rm = TRUE),
    sePupil=sd(avg.pupilSs, na.rm = TRUE)/sqrt(length(avg.pupilSs))
  )

#only care about A1V1, A2V2, A3-- or 1,2,5
doo3<-doo2[!(doo2$trialtype==3 | doo2$trialtype==4 | doo2$trialtype==6),]
doo3$label <- doo3$trialtype
doo3$label[doo3$trialtype==5] <- 1 #trialtype5 = A3--
doo3$label[doo3$trialtype==1] <- 3 #trialtype1 = A1V1

#facet wrap
label <- c(`1` = "First block",`5` = "Last block")
doo4 <- subset(doo3, label > 1)

ggplot(doo4,aes(x=TIMECODE,y=avg.pupil,fill=factor(label),colour=factor(label)))+
  geom_line()+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  facet_wrap(~block,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_manual(values=c("#ff15ff", "#559455"),name="Trial type",breaks=c("2","3"),labels=c("High uncertainty, moderate reward","Low uncertainty, high reward"))+
  scale_y_continuous(labels=percent,limits=c(-0.1,.15),breaks=seq(-0.1,.15,0.05))+
  theme(legend.position = "bottom")

#all trialtypes
label <- c(`1` = "A1V1",`2` = "A2V2",`3` = "A2--",`4` = "--V2",`5` = "A3--",`6` = "--V3")
ggplot(doo2,aes(x=TIMECODE,y=avg.pupil,fill=factor(block),colour=factor(block)))+
  geom_line()+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Time (ms)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  facet_wrap(~trialtype,nrow = 3,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels=percent,limits=c(-0.1,.15),breaks=seq(-0.1,.15,0.05))+
  theme(legend.position = "bottom")+scale_color_brewer()

```

#cue = baseline, outcome = audio

trial types: trialtype (1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
average PDR
X: block
Y: pupil change
facet wrap by trial type
```{r}
#only care about first 4000ms
#2s + 4.6s min
poo5 <- subset(poo4, TIMECODE < 1001) #just audio
poo5$block <- 1 #12
poo5$block[poo5$timesseen > 3 & poo5$timesseen < 7] <- 2 #4 5 6
poo5$block[poo5$timesseen > 6 & poo5$timesseen < 10] <- 3 #7 8 9
poo5$block[poo5$timesseen > 9 & poo5$timesseen < 13] <- 4 #10 11 12
poo5$block[poo5$timesseen > 12] <- 5 #13 14 15

doo <- group_by(poo5,subID,block,trialtype) %>%
  summarise(
    avg.pupilSs=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
doo2 <- group_by(doo,block,trialtype) %>%
  summarise(
    avg.pupil=mean(avg.pupilSs,na.rm = TRUE),
    sePupil=sd(avg.pupilSs, na.rm = TRUE)/sqrt(length(avg.pupilSs))
  )

#only care about A1V1, A2V2, A3-- or 1,2,5
doo3<-doo2[!(doo2$trialtype==3 | doo2$trialtype==4 | doo2$trialtype==6),]
doo3$label <- doo3$trialtype
doo3$label[doo3$trialtype==5] <- 1 #trialtype5 = A3--
doo3$label[doo3$trialtype==1] <- 3 #trialtype1 = A1V1

#facet wrap
label <- c(`1` = "Low uncertainty, low reward",`2` = "High uncertainty, moderate reward",`3` = "Low uncertainty, high reward")

ggplot(doo3,aes(x=block,y=avg.pupil,fill=factor(label),colour=factor(label)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials per block)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(-0.05,.15),breaks=seq(-0.05,0.15,0.02))+
  theme(legend.position="none")+
  facet_wrap(~label,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_fill_manual(values=c("#2a92ff", "#ff15ff", "#559455"))+
  scale_color_manual(values=c("#2a92ff", "#ff15ff", "#559455"))

#all trialtypes
#(1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
label <- c(`1` = "A1V1",`2` = "A2V2",`3` = "A2--",`4` = "--V2",`5` = "A3--",`6` = "--V3")

ggplot(doo2,aes(x=block,y=avg.pupil,fill=factor(trialtype),colour=factor(trialtype)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials/block)", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(legend.position="none")+
  facet_wrap(~trialtype,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_y_continuous(labels=percent,limits=c(-0.1,.15),breaks=seq(-0.1,0.15,0.05))

```

#cue = baseline, outcome = audio+visual

trial types: trialtype (1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
average PDR
X: block
Y: pupil change
facet wrap by trial type
```{r}
#only care about first 4000ms
#2s + 4.6s min
poo5 <- subset(poo4, TIMECODE < 2001) #just audio + visual
poo5$block <- 1 #12
poo5$block[poo5$timesseen > 3 & poo5$timesseen < 7] <- 2 #4 5 6
poo5$block[poo5$timesseen > 6 & poo5$timesseen < 10] <- 3 #7 8 9
poo5$block[poo5$timesseen > 9 & poo5$timesseen < 13] <- 4 #10 11 12
poo5$block[poo5$timesseen > 12] <- 5 #13 14 15

doo <- group_by(poo5,subID,block,trialtype) %>%
  summarise(
    avg.pupilSs=mean(PUPIL_CORRECTED,na.rm = TRUE)
  )
doo2 <- group_by(doo,block,trialtype) %>%
  summarise(
    avg.pupil=mean(avg.pupilSs,na.rm = TRUE),
    sePupil=sd(avg.pupilSs, na.rm = TRUE)/sqrt(length(avg.pupilSs))
  )

#only care about A1V1, A2V2, A3-- or 1,2,5
doo3<-doo2[!(doo2$trialtype==3 | doo2$trialtype==4 | doo2$trialtype==6),]
doo3$label <- doo3$trialtype
doo3$label[doo3$trialtype==5] <- 1 #trialtype5 = A3--
doo3$label[doo3$trialtype==1] <- 3 #trialtype1 = A1V1

#facet wrap
label <- c(`1` = "Low uncertainty, low reward",`2` = "High uncertainty, moderate reward",`3` = "Low uncertainty, high reward")

ggplot(doo3,aes(x=block,y=avg.pupil,fill=factor(label),colour=factor(label)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials per block)", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_y_continuous(labels=percent,limits=c(-0.05,.15),breaks=seq(-0.05,0.15,0.02))+
  theme(legend.position="none")+
  facet_wrap(~label,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_fill_manual(values=c("#2a92ff", "#ff15ff", "#559455"))+
  scale_color_manual(values=c("#2a92ff", "#ff15ff", "#559455"))

#all trialtypes
#(1=A1V1, 2=A2V2, 3=A2--, 4=--V2, 5=A3--, 6=--V3)
label <- c(`1` = "A1V1",`2` = "A2V2",`3` = "A2--",`4` = "--V2",`5` = "A3--",`6` = "--V3")

ggplot(doo2,aes(x=block,y=avg.pupil,fill=factor(trialtype),colour=factor(trialtype)))+
  geom_errorbar(colour="black", width=.1, aes(ymin=avg.pupil-sePupil, ymax=avg.pupil+sePupil))+
  geom_point(shape=21, size=4)+
  ggtitle("Pupil change")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Block (3 trials/block)", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(legend.position="none")+
  facet_wrap(~trialtype,nrow = 1,labeller = as_labeller(label))+
  theme(strip.text = element_text(size=16))+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_smooth(method=lm,se=FALSE)+
  scale_y_continuous(labels=percent,limits=c(-0.1,.15),breaks=seq(-0.1,0.15,0.05))

```